\TheTitle

### 2017-06-12 paper/userstudy.tex
Resizing text width
84-wide text doesn't fit split-screen on my little monitor.
Resizing it down to 72-wide.
Figure: Merges over total commits
Shows the nearly linear relationship between commits and merges.
Was not actually expecting this.

% TODO: Finish the paragraph on complexity
The complexity of the merge trees varies greatly.

The complexity of these trees varies greatly as well, . % TODO: Finish this sentence

>>>>

% TODO: Finish the paragraph on complexity
The complexity of the merge trees varies greatly as shown in
figure~\ref{fig:merge_vs_commits}, which shows that as the number of
commits increases in a merge-tree, the number of merges also increases
nearly linearly.

\begin{figure}[htpb]
  \centering
  \begin{tikzpicture}
    \begin{axis} [
      ylabel=Total Merges,
      xlabel=Total Commits,
      grid=both
      ]
      \addplot[chartblue] table[col sep=comma, x index={1}, y index={2}] {data/merge_counts.csv};
    \end{axis}
  \end{tikzpicture}
  \caption{Comparison between the number commits and the number of merge commits}
  \label{fig:merge_vs_commits}
\end{figure}
